MTB Expression Analysis

### 2018-01-12 analysis/MTB_Expression_Analysis.Rmd
wflow_publish("MTB_Expression_Analysis.Rmd")

At 18 hours post-infection, There are eight bacterial infections: "Rv.18", "Rv+.18", "GC.18", "BCG.18", "Smeg.18", "Yers.18", "Salm.18", "Staph.18". Here we set $K=5$, the same like [Blischak, et al, 2015](https://www.nature.com/articles/srep16882). The motifs are shown below.

@@

S3 = read.csv("../data/S3.csv",
              header = FALSE,stringsAsFactors = FALSE)
id = rownames(dat_cpm)
lfsr18 = z18_k5$lfsr[[1]][,1] 
list = id[lfsr18<0.01]
a = intersect(S3[,2],list)
print(gene_names[a])
```

>>>>

At 18 hours post-infection, There are eight bacterial infections: "Rv.18", "Rv+.18", "GC.18", "BCG.18", "Smeg.18", "Yers.18", "Salm.18", "Staph.18". Here we set $K=5$, the same as [Blischak et al, 2015](https://www.nature.com/articles/srep16882). The learned motifs are shown below.

@@

S3 = read.csv("../data/S3.csv",header = FALSE,stringsAsFactors = FALSE)
id = names(gene_names)
ll = intersect(S3[,2],id)
lfsr18 = z18_k5$lfsr[[1]][,1] 
list = id[lfsr18<0.01]
a = intersect(S3[,2],list)
print(gene_names[a])
```
